\vskip-0.6in Temporary Trade Barriers: When Will They End?

### 2017-11-10 draft.tex
finish abstract and conclusion

\begin{quote}
{Abstract

@@

Given that the industry receives temporary protection in the first phase of interaction, there will be another phase of interaction when the trade barrier expires, here modeled as five years later to match the typical five years sunset provision for antidumping duties under the WTO. At this point, the interaction is similar to that during the first phase, with the industry first exerting effort and then the ITC deciding whether to extend the temporary trade barrier or to revert to the MFN tariff. The essential strategic difference is that at this point the level of the temporary trade barrier is taken as exogenously set at the level determined in the first round of interaction. It is the second phase that is modeled in the current paper, with the addition of the first phase acknowledged as a very important and imminent extension.

@@

\subsection{Outline}

\vskip.2in
\begin{itemize}
	\item Authorized by WTO
	\item Very little in the agreements to guide the process
		\begin{itemize}
			\item WTO litigation gives gov'ts a LOT of latitude
			\item Renewal decision determined by complex process including DOC, ITC, pressure via other political bodies.
		\end{itemize}
	\item In U.S., for AD:
		\begin{itemize}
			\item DOC initiates, determines whether dumping would continue
						\begin{itemize}
			\item Can renew AD duties
			\item Susceptible to influence of lobbying, perhaps both direct and indirect
			\item Modeled in reduced form
		\end{itemize}

			\item ITC determines whether injury would recur / continue
		\end{itemize}
\end{itemize}

\vskip.2in
The probability that an AD duty gets renewed

\begin{itemize}
	\item Increases in lobbying effort
	\item Decreases in the MFN tariff
	\item Is invariant to the trading partner's tariff
	\item Increases in the profitability of the import-competing sector
	\item Increases in the strength of the lobby
	\item May be concave in the AD duty
\end{itemize}

There is much to be learned about the workings of the world trading system by examining the duration of deviations from base tariff commitments. I plan a project whose first stage is theoretical with a second, later stage in which the theory is tested on a data set of renewal decisions for anti-dumping measures.

\subsection{Related Literature}
\textbf{WILL NEED MAJOR OVERHAUL}

Kara Reynold's ``Political Economy of Antidumping Reviews (Shushanik)

@@

Mansfield, Milner and Rosendorff (2000) study the impact of executive/legislative interactions on international agreements in the case of exogenously-determined preferences. They show that democracies trade more with each other because the domestic legislature only cooperates if the foreign government makes deep tariff cuts. Ethier (2002) treats the effect of a separation of powers between trade negotiators and the government officials who administer protection.

Milner and Rosendorff (1997) explore how uncertainty can affect trade policy and ratification failure when political preferences, and therefore uncertainty, are exogenous. In Le Breton and Salanie (2003), the lobby is uncertain about the preferences of a unitary decision maker. Le Breton and Zaporozhets (2007) replace the unitary decision maker with a legislature with multiple actors. In Song (2008), policy-making power is shared between an executive and a unitary legislature. The lobbies influence the preferences of the legislature in a context of unilateral policy making with no uncertainty, and Coates and Ludema (2001) study trade policy leadership with endogenous lobbying in the presence of political uncertainty with imperfect monitoring.

@@

\textbf{REVISE EXTENSIVE FORM}

@@

Figure~\ref{fig:ext} illustrates the timing of the game. Taking the trade-agreement tariffs $\bta = \left(\tau^a,\tau^{*a}\right)$\footnote{I use the convention throughout of representing a vector of tariffs for both countries $(\tau,\tau^*)$ as a single bold $\bm{\tau}$.} and the antidumping duty level $\tad$ as given, the import-competing firms jointly attempt to persuade the government agency to renew the antidumping duties by choice of lobbying effort $e$.

@@

Lobby must be able to trigger the original AD duty
\begin{itemize}
	\item \textit{Can} think of non-adherence to MFN as eqm path dispute
	\item It could be justified, not motivated by politics/rent-seeking
	\item But still, firms lobby for duties they don't get
\end{itemize}

@@

\begin{itemize}
	\item Strength of evidence
	\item Probability foreign will retaliate or initiate dispute (indirect)
	\item $G$'s valuation of harm to industry, e.g. how politically important is industry?
	\item Uncertainty could be, in part, about how mobile labor is (Kishore)
\end{itemize}

@@

@@

\begin{assumption}
  $\ta$ is uniformly distributed on some $\Theta=\left[\underline{\ta},\overline{\ta}\right]$.
  \label{as:ta}
\end{assumption}

Assumption~\ref{as:ga_c} means that the government agency favors the import-competing industry more the higher is its lobbying effort, but that there are diminishing returns to lobbying activity. It rules out higher effort making lower weights more likely and that the structure of uncertainty changes with increasing effort so that higher weights become more likely at an accelerating pace. Assumption~\ref{as:ga_ta} simply provides for an intuitive labeling so that larger realizations of $\ta$ increase the value of the political economy weight.

@@

\subsection{Information and Equilibrium Selection}
\label{sec:info}

@@

I examine a simple class of equilibria that have three key features. First, information about political uncertainty is symmetric. However, in line with the literature, I assume the lobby's contribution is not observable to the foreign legislature. Thus the influence of one country's lobby on the other country's legislature occurs only through the tariffs selected.\footnote{cfr. Grossman and Helpman (1995b), page 685.} Since players in the same country can take advantage of more information than those who are in different countries, the solution concept is perfect public equilibrium (PPE).

@@

Finally, I assume that an external authority can ensure enforcement of the agreement.

@@

Because the duties are a unilateral policy that we presume here are permissable under WTO rules, the decision to renew the duties or not does not change the level of the tariff applied by the foreign trading partner. That is, there is no incentive in terms of reciprocal treatment to deter the home government from renewing the duties.

@@

The level at which the antidumpting duties are set is likely to be related to some of the variables under consideration here, as the duties are determined five (or more) years earlier through a process similar to the renewal process. Endogenizing the level of the antidumping duties, as well as the fact of their application in the first place, is planned as an important extension.

@@

\begin{result}
	The total probability that the antidumping duties will be renewed is increasing in $\ga(\cdot)$ if the direct effect dominates and is decreasing in $\ga(\cdot)$ if the indirected effect dominates. \hyperlink{Pr_ga_total}{Proof}
	\label{res:ga_total}
\end{result}

@@

\section{Conclusion}
\label{sec:concl}

			Future Work

An important question in this model is why an industry that receives protection as a result of the original interaction concerning the imposition of the temporary trade barrier would fail to get it renewed. At the most basic level, if we assume the industry faces the same uncertainty and responds in the same way, it could get a different draw and thus a different outcome. Moreover, having the level of the temporary trade barrier set by the original interaction serves to reduce the industry's incentive to exert effort on the margin.

In addition, some factors that affect both the ITC's and the industry's decision-making can change significantly over the course of a five-year period. Most of these factors display at least some variation across industries.

Because a temporary trade barrier insulates an industry from competition, when receiving such protection, an industry should be able to increase profits. The amount that profits increase will vary by industry, and the decisions about how to use the extra profits will also plausibly vary. Some industries may use this opportunity to become more competitive and thus less interested in seeking protection while others may use the added profits to become more politically powerful and thus better able to gain future protection. These decisions, and the basic question of whether protection and technological upgrading are complements or substitutes, feeds back into the decision-making process of the ITC.

Another interesting dimension along which there is uncertainty for the ITC is in its evaluation of the probability with which trading partners will dispute or retaliate against a temporary trade barrier. This not only varies across temporary trade barriers, but may vary across time. In particular, the ITC can observe whether a dispute has been filed during the first five years of a temporary trade barrier and update its beliefs about future retaliation in a way that varies across industries.

\begin{itemize}
	\item Comparative static on uncertainty measure
	\item Empirical work
	\item Extend model to include initial decision to grant protection.
		\begin{itemize}
			\item Explain variation in a lobby's incentives between original application of AD and renewal
			\item Lobby's choice between investing in productive vs. rent-seeking behavior while protected
			\item Need to have first stage (Jee-Hyeong, Gary Lyn)
		\begin{itemize}
			\item Look at Park and Blonigen (Jee-Hyeong)
			\item Cost differential for firms to get initial duty vs. renewal?
			\item Some firms choose not to pursue renewal when DOC contacts them 30-days before (Sasha)
		\end{itemize}
	\item Lobbying effort may be endogenous: if prob. of success is lower, maybe it's not worth providing effort (Mostafa)
		\end{itemize}
\end{itemize}

@@

This can be simplied to
\begin{equation}
  \frac{\left[\mathit{CS}_X(\tad) + \mathit{TR}(\tad)  -\mathit{CS}_X(\tau^a) - \mathit{TR}(\tau^a) \right]\left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right) }{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
\label{appex:pi}
\end{equation}

>>>>

\begin{quote}
{Under WTO law, temporary trade barriers such as antidumping duties must be removed after a period of four or five years. However, under rather vague legal conditions, they can be renewed. This institutional environment provides the structure to carefully study the determinants of the \textit{length} of protection. We present a theoretical political-economy model of the renewal process and find that the probability a temporary trade barrier will be renewed decreases in the level of trade agreement tariffs and is also likely to decrease in the level of the anti-dumping duties. An increase in an industry's profitability is shown to increase the probability of renewal also increases. Lobbying effort also increases the probability for a fixed strength of the lobby, while the strength of the lobby itself has more nuanced effects on the renewal probability.

@@

Given that the industry receives temporary protection in the first phase of interaction and the protection remains in place until expiry, there will be another phase of interaction when the trade barrier expires, here modeled as five years later to match the typical five years sunset provision for antidumping duties under the WTO. At this point, the interaction is similar to that during the first phase, with the industry first exerting effort and then the government deciding whether to extend the temporary trade barrier or to revert to the MFN tariff. The essential strategic difference is that at this point the level of the temporary trade barrier is taken as exogenously set at the level determined in the first round of interaction. It is the second phase that is modeled in the current paper, with the addition of the first phase acknowledged as a very important and imminent extension.

@@

Interestingly, there are very few stipulations in the General Agreement on Tariffs and Trade (GATT) / World Trade Organization (WTO) to guide the renewal process. WTO-level litigation has not provided significant additional structure, so governments appear to have significant latitude in their decision-making process regarding renewals of temporary trade barriers. These decisions are often made via complex processes, adding to uncertainty.

In the United States, for the renewal of antidumping duties, the Department of Commerce must initiate a renewal proceeding and determine whether dumping would continue of the duties are not renewed. The International Trade Commission determines whether injury would recur or continue. These bodies are likely susceptible to the influence of lobbying both directly from industry and consumer groups and indirectly via other political bodies such as Congress as well as other parts of the Executive branch.

Given this complicated decision-making process with few guidelines provided at the international level, I present a theoretical model to guide our thinking about what elements impact renewal decisions. I find that the probability that antidumping duties will be renewed is invariant to foreign tariffs, decreases in most-favored nation tariffs and is likely to decrease in the level of the anti-dumping duties. The probability increases in lobbying effort, but the overall impact of the strength of the lobby depends on whether the positive direct effect outweighs the negative indirect effect on the lobby's incentives. If the industry becomes more (less) profitable in the sense that the gap between profits under the antidumping duties and profits under the trade agreement tariffs increases (decreases), the probability of renewal also increases.

There is much to be learned about the workings of the world trading system by examining the duration of deviations from base tariff commitments. After extending this model to include the stage at which antidumping duties are set, I plan to take this model to a data set of renewal decisions for anti-dumping measures.

\begin{comment}
\subsection{Related Literature}
\textbf{WILL NEED MAJOR OVERHAUL}

%Kara Reynold's ``Political Economy of Antidumping Reviews (Shushanik)

@@

Milner and Rosendorff (1997) explore how uncertainty can affect trade policy and ratification failure when political preferences, and therefore uncertainty, are exogenous. In Le Breton and Salanie (2003), the lobby is uncertain about the preferences of a unitary decision maker. Le Breton and Zaporozhets (2007) replace the unitary decision maker with a legislature with multiple actors. In Song (2008), policy-making power is shared between an executive and a unitary legislature. The lobbies influence the preferences of the legislature in a context of unilateral policy making with no uncertainty, and Coates and Ludema (2001) study trade policy leadership with endogenous lobbying in the presence of political uncertainty with imperfect monitoring.
\end{comment}

@@

\begin{comment}
\textbf{REVISE EXTENSIVE FORM}

@@

Figure~\ref{fig:ext} illustrates the timing of the game.
\end{comment}

 Taking the trade-agreement tariffs $\bta = \left(\tau^a,\tau^{*a}\right)$\footnote{I use the convention throughout of representing a vector of tariffs for both countries $(\tau,\tau^*)$ as a single bold $\bm{\tau}$.} and the antidumping duty level $\tad$ as given, the import-competing firms jointly attempt to persuade the government agency to renew the antidumping duties by choice of lobbying effort $e$.

@@

\begin{comment}
Lobby must be able to trigger the original AD duty
\begin{itemize}
	\item \textit{Can} think of non-adherence to MFN as eqm path dispute
	\item It could be justified, not motivated by politics/rent-seeking
	\item But still, firms lobby for duties they don't get
\end{itemize}

@@

\begin{itemize}
	\item Strength of evidence
	\item Probability foreign will retaliate or initiate dispute (indirect)
	\item $G$'s valuation of harm to industry, e.g. how politically important is industry?
	\item Uncertainty could be, in part, about how mobile labor is (Kishore)
\end{itemize}
\end{comment}

@@

Although political uncertainty is important in informing the lobby's behavior, the player that has more information moves last in the game so subgame perfect Nash equilibrium is the appropriate solution concept.

@@

\begin{assumption}
  The pdf of the induced distribution on $\ga(e,\ta)$ is weakly increasing in $e$.
  \label{as:ta}
\end{assumption}

Assumption~\ref{as:ga_c} means that the government agency favors the import-competing industry more the higher is its lobbying effort, but that there are diminishing returns to lobbying activity. It rules out higher effort making lower weights more likely and that the structure of uncertainty changes with increasing effort so that higher weights become more likely at an accelerating pace. Assumption~\ref{as:ga_ta} simply provides for an intuitive labeling so that larger realizations of $\ta$ increase the value of the political economy weight. Assumption~\ref{as:ta} is a restriction either on the distribution of uncertainty or on how it enters $\ga(e,\cdot)$ so that higher values of the political economy weight become more likely at higher values of lobbying effort.

@@

\begin{comment}
\subsection{Information and Equilibrium Selection}
\label{sec:info}

@@

@@

Finally, I assume that an external authority can ensure enforcement of the agreement.
\end{comment}

@@

Because the duties are a unilateral policy that we presume here are permissible under WTO rules, the decision to renew the duties or not does not change the level of the tariff applied by the foreign trading partner. That is, there is no incentive in terms of reciprocal treatment to deter the home government from renewing the duties.

@@

The level at which the antidumping duties are set is likely to be related to some of the variables under consideration here, as the duties are determined five (or more) years earlier through a process similar to the renewal process. Endogenizing the level of the antidumping duties, as well as the fact of their application in the first place, is planned as an important extension.

@@

\begin{result}
	The total probability that the antidumping duties will be renewed is increasing in $\ga(\cdot)$ if the direct effect dominates and is decreasing in $\ga(\cdot)$ if the indirect effect dominates. \hyperlink{Pr_ga_total}{Proof}
	\label{res:ga_total}
\end{result}

@@

\section{Conclusion}
\label{sec:concl}
This is very much work in progress. The next stage is to extend the model to include the initial decision to grant protection. This is important because of course the imposition of the original protective measure is related to the incentives to renew it, so the endogeneity should be taken into account.

What's more, we'd like to know why an industry that receives protection as a result of the original interaction concerning the imposition of the temporary trade barrier would fail to get it renewed---or, even more interesting, choose not to pursue a renewal when contacted by the Department of Commerce just before the antidumping duties expire. At the most basic level, if we assume the industry faces the same uncertainty and responds in the same way, it could get a different draw and thus a different outcome. Moreover, having the level of the temporary trade barrier set by the original interaction serves to reduce the industry's incentive to exert effort on the margin.

In addition, some factors that affect both the government's and the industry's decision-making can change significantly over the course of a five-year period. Most of these factors display at least some variation across industries.

Because a temporary trade barrier insulates an industry from competition, when receiving such protection, an industry should be able to increase profits. The amount that profits increase will vary by industry, and the decisions about how to use the extra profits will also plausibly vary. Some industries may use this opportunity to become more competitive and thus less interested in seeking protection while others may use the added profits to become more politically powerful and thus better able to gain future protection. These decisions, and the basic question of whether protection and technological upgrading are complements or substitutes, feeds back into the decision-making process of the government.

Another interesting dimension along which there is uncertainty for the government is in its evaluation of the probability with which trading partners will dispute or retaliate against a temporary trade barrier. This not only varies across temporary trade barriers, but may vary across time. In particular, the government can observe whether a dispute has been filed during the first five years of a temporary trade barrier and update its beliefs about future retaliation in a way that varies across industries.

All of this will then be taken to the data in the form of the World Bank's Temporary Trade Barriers Database.

@@

This can be simplified to
\begin{equation}
  \frac{\left[\mathit{CS}_X(\tad) + \mathit{TR}(\tad)  -\mathit{CS}_X(\tau^a) - \mathit{TR}(\tau^a) \right]\left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right) }{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
\label{appex:pi}
\end{equation}
